Dependent Object Types

### 2012-08-06 article.tex
all cases
air
cleanup of proof

>>>>

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$. For
each case, we need to show $t \in \rele k \Gamma - T, \forall k$. The
non-trivial case is to need to show ${t'} \in \relv {k-j-1} {\Gamma'}
{s'} T$ by supposing $k > 0$, $s \in \rels k \Gamma -$, and, for some
$j \leq k$, $\reductionl {t} s {t'} {s'} j \andl \irred {t'}
{s'} \andl \Gamma' \in \relg \Gamma k {s'} \Gamma$.

\ \\

\Case \textsc{var}: $\Gamma \ts x : T$ knowing $(x : T) \in
\Gamma$. $x \in \relv {k-1} \Gamma s T$ follows from the definition of
$\mathcal{G}$.

\ \\

\Case \textsc{sel}: $\Gamma \ts t_1.l_i : T$ knowing $\Gamma \ts t_1 :
T_1$, $\Gamma \ts T_1 \expand_z \seq{D}$, $\ldecl {l_i} {V_i} \in
\seq{D}$ and knowing either that $t_1 = p_1 \andl T = \subst p z
    {V_i}$ or that $z \not\in \fn(V_i) \andl T = V_i$.

%Need to show $t_1.l_i \in \rele k \Gamma - T$. Suppose $k > 0$ and $s
%\in \rels k \Gamma -$. Suppose, for some $j \leq k$, $\reductionl
%    {t_1.l_i} s {t'} {s'} j \andl \irred {t'} {s'} \andl \Gamma' \in
%    \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in \relv
%          {k-j-1} {\Gamma'} {s'} T$.

By operational semantics and induction hypothesis, $\reductionl {t_1}
s {t_1'} {s'} {j-1}$ and $\irred {t_1'} {s'}$ and ${t_1'} \in \relv
{k-j+1-1} {\Gamma'} {s'} {T_1}$.

By operational semantics, $\reductionl {t_1'.l_i} {s'} {t'} {s'}
1$. Since ${t_1'} \in \relv {k-j} {\Gamma'} {s'} {T_1}$, we can
conclude $t' \in \relv {k-j-1} {\Gamma'} {s'} T$ from the clause for
value labels.

\ \\

\Case \textsc{msel}: $\Gamma \ts t_1.m_i(t_2) : T$ knowing $\Gamma \ts
t_1 : T_1$, $\Gamma \ts t_2 : T_2$, $\Gamma \ts T_1 \expand_z
\seq{D}$, $\mdecl {m_i} {S_i} {U_i} \in \seq{D}$ and knowing either
that $t_1 = p_1 \andl S = \subst p z {S_i} \andl T = \subst p z {U_i}$
or that $z \not\in \fn(S_i) \andl z \not\in \fn(U_i) \andl S = S_i \andl
T = U_i$.

%Need to show $t_1.m_i(t_2) \in \rele k \Gamma - T$. Suppose $k > 0$
%and $s \in \rels k \Gamma -$. Suppose, for some $j \leq k$,
%$\reductionl {t_1.m_i(t_2)} s {t'} {s'} j \andl \irred {t'} {s'} \andl
%\Gamma' \in \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in
%\relv {k-j-1} {\Gamma'} {s'} T$.

By operational semantics and induction hypotheses, $\reductionl {t_1}
s {t_1'} {s_1} {j_1}$ and $\irred {t_1'} {s_1}$ and $\reductionl {t_2}
{s} {t_2'} {s_2} {j_2}$ and $\irred {t_2'} {s_2}$ and ${t_1'} \in
\relv {k-j_1-1} {\Gamma_1} {s_1} {T_1}$ and ${t_2'} \in \relv
{k-j_2-1} {\Gamma_2} {s_2} {T_2}$.

Because $t_2$ reduces to a value $t_2'$ starting in store $s$, it
should also reduce to a value $v_2$ in the same number of steps
starting in store $s_1$, since $s_1$ includes $s$. So let $\reductionl
{t_2} {s_1} {v_2} {s_{12}} {j_2}$ with $v_2 \in \relv {k-j_2-1}
{\Gamma_{12}} s_{12}$.

By operational semantics, $\reductionl {t_1'.m_i(v_2)} {s_{12}}
{\subst {v_2} {x_i} {t_i}} {s_{12}} 1$.

It remains to show that ${\subst {v_2} {x_i} {t_i}} \in \rele
{k-j_2-j_2-1} {\Gamma_{12}} {s_{12}} {T}$ to complete the case. We
defer this to the substitution lemma.

\ \\

\Case \textsc{new}: $\Gamma \ts \new y c {t_b} : T$ knowing ...

%Need to show $\new y c {t'} \in \rele k \Gamma - T$. Suppose $k > 0$
%and $s \in \rels k \Gamma -$. Suppose, for some $j \leq k$,
%$\reductionl {\new y c {t'}} s {t''} {s''} j \andl \irred {t''} {s''} \andl
%\Gamma'' \in \relg \Gamma k {s''} \Gamma$. Remains to show ${t''} \in
%\relv {k-j-1} {\Gamma''} {s''} T$.

By operational semantics, $\reductionl {\new y c {t_b}} s {t_b} {s_b} 1$
where $s_b = s \envplus{y \mapsto c}$. So $\reductionl {t_b} {s_b} {t'}
{s'} {j-1}$.

By induction hypotheses, $y \in \relv k {\Gamma_b} {s_b} {T_c}$ and $t_b \in
\rele e k {\Gamma_b} {s_b}$.

Result follows by monotonicity of $\mathcal{V}$.

\end{myproof}

\subsection{Proof of the Substitution Lemma}

\todo{statement and proof}
